This is the title : v\versionnumber

### 2018-06-15 templates/livecoms-template-bestpractices.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,lessons]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Include "pubversion" option when the volume/article/DOI information is known
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Lessons Learned document.
Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

Here you would explain what problem you are tackling and briefly motivate your work.
Since a Lessons Learned document provides negative results in a particular category, you will want to clearly define your category and also motivate the application of your work to your particular problem.

We suggest that you envision your document potentially extending in the future to include other Lessons Learned in the same category, so you may want to organize your work in a way which would allow this type of extension (e.g. providing a general introduction then using subsections to explain your particular problem) -- for example, describing potential of mean force calculations generally, then in a subsection motivating your particular application of them.

@@

A Lessons Learned document is a regular scientific article, and should be prepared with similar organization.
Sample typical section headers follow.

\section{Theory and Methods}

You should use a section (or separate sections, if this yields better organization) to describe the theory and methods relevant to your work.

This should include all information required for a reader to reproduce the results, including software version numbers and links to any in-house files or scripts

\section{Results}

You would give your results here.
Since the goal here is not just to present negative results, but also to provide lessons learned from doing so, you will want to make sure you have data to show why your approach failed.

\section{Discussion}

Discussion should highlight the lessons learned and give tips for avoiding future mistakes.
Try to tell readers what you wish you had known before starting.

\section{Conclusions}

Give conclusions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,bestpractices]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Include "pubversion" option when the volume/article/DOI information is known
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Best Practices document. Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

Here you would explain what problem you are tackling and briefly motivate your work.

@@

\section{Prerequisites}

Here you would identify prerequisites/background knowledge that are assumed by your work and your checklist which you view as critical, ideally giving links to good sources on these topics.
Checklists are normally focused on errors made by users with training and experience in molecular simulations, so you can assume a basic familiarity with the fundamentals of molecular simulations.

\section{Checklist}
Here we use a full-page checklist with multiple sections, so it will appear on a separate page of the sample PDF.
Other checklist formats are possible, as shown in the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates}.

Your checklist should include a succinct list of steps that people should follow when carrying out the task in question.
This is provided to ensure certain basic standards are followed and common but critical major errors are avoided.
Note that a checklist is not intended to cover \emph{all} important steps, but rather focus on the most common reasons for failure or incorrect results, or issues which are particularly crucial.

% This provides a checklist which
% - spans a full page
% - consists of multiple sub-checklists
% - exists on a separate page
% This style of checklist will be especially helpful if you want to encourage readers to print and use your checklist in practice, as they
% can easily print it without also printing other material from your manuscript. However, other styles of checklist are also possible (below).
\begin{Checklists*}[p!]

\begin{checklist}{First list}
\textbf{You can easily make full width checklists that take a whole page}
\begin{itemize}
\item Items in your checklist can and should reference sections where the cited issues are discussed in detail, such as Section~\ref{sec:reference_this}
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Second list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Third list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Fourth list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\end{Checklists*}

\section{Rationale}

Your Rationale section, or sections, can follow or precede your checklist (we expect that often, following the checklist will be preferable) and provide the necessary rationale for the checklist, and act as more complete \emph{best practices} description.
This should include 1) significant detail as to the possible alternative ways to accomplish a given task, 2) description of advantages and disadvantages of the various approaches, and 3) significant literature documentation about reasons for choices.

\subsection{Algorithms and Pseudocode}
\label{sec:reference_this}

The \texttt{algpseudocode} and \texttt{algorithms} packages is loaded by the document class. \ALG{euclid} was taken directly from the package documentation. (Please do not load \texttt{algorithm2e}; it's not compatible with \texttt{algpseudocde} nor \texttt{algorithms}!)

\begin{algorithm}
\caption{Euclid's algorithm}\label{alg:euclid}
\begin{algorithmic}%[1]  %% uncomment to enable line numbers
\Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
   \State $r\gets a\bmod b$
   \While{$r\not=0$}\Comment{We have the answer if r is 0}
      \State $a\gets b$
      \State $b\gets r$
      \State $r\gets a\bmod b$
   \EndWhile\label{euclidendwhile}
   \State \textbf{return} $b$\Comment{The gcd is b}
\EndProcedure
\end{algorithmic}
\end{algorithm}

### 2018-06-15 templates/livecoms-template-tutorials.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,bestpractices]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Include "pubversion" option when the volume/article/DOI information is known
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Best Practices document. Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

@@

Here you would identify prerequisites/background knowledge that are assumed by your work and your checklist which you view as critical, ideally giving links to good sources on these topics.
Checklists are normally focused on errors made by users with training and experience in molecular simulations, so you can assume a basic familiarity with the fundamentals of molecular simulations.

\section{Checklist}
Here we use a full-page checklist with multiple sections, so it will appear on a separate page of the sample PDF.
Other checklist formats are possible, as shown in the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates}.

Your checklist should include a succinct list of steps that people should follow when carrying out the task in question.
This is provided to ensure certain basic standards are followed and common but critical major errors are avoided.
Note that a checklist is not intended to cover \emph{all} important steps, but rather focus on the most common reasons for failure or incorrect results, or issues which are particularly crucial.

% This provides a checklist which
% - spans a full page
% - consists of multiple sub-checklists
% - exists on a separate page
% This style of checklist will be especially helpful if you want to encourage readers to print and use your checklist in practice, as they
% can easily print it without also printing other material from your manuscript. However, other styles of checklist are also possible (below).
\begin{Checklists*}[p!]

\begin{checklist}{First list}
\textbf{You can easily make full width checklists that take a whole page}
\begin{itemize}
\item Items in your checklist can and should reference sections where the cited issues are discussed in detail, such as Section~\ref{sec:reference_this}
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Second list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Third list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Fourth list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\end{Checklists*}

\section{Rationale}

Your Rationale section, or sections, can follow or precede your checklist (we expect that often, following the checklist will be preferable) and provide the necessary rationale for the checklist, and act as more complete \emph{best practices} description.
This should include 1) significant detail as to the possible alternative ways to accomplish a given task, 2) description of advantages and disadvantages of the various approaches, and 3) significant literature documentation about reasons for choices.

\subsection{Algorithms and Pseudocode}
\label{sec:reference_this}

The \texttt{algpseudocode} and \texttt{algorithms} packages is loaded by the document class. \ALG{euclid} was taken directly from the package documentation. (Please do not load \texttt{algorithm2e}; it's not compatible with \texttt{algpseudocde} nor \texttt{algorithms}!)

\begin{algorithm}
\caption{Euclid's algorithm}\label{alg:euclid}
\begin{algorithmic}%[1]  %% uncomment to enable line numbers
\Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
   \State $r\gets a\bmod b$
   \While{$r\not=0$}\Comment{We have the answer if r is 0}
      \State $a\gets b$
      \State $b\gets r$
      \State $r\gets a\bmod b$
   \EndWhile\label{euclidendwhile}
   \State \textbf{return} $b$\Comment{The gcd is b}
\EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LIVECOMS ARTICLE TEMPLATE FOR BEST PRACTICES GUIDE
%%% ADAPTED FROM ELIFE ARTICLE TEMPLATE (8/10/2017)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PREAMBLE
\documentclass[9pt,tutorial]{livecoms}
% Use the 'onehalfspacing' option for 1.5 line spacing
% Use the 'doublespacing' option for 2.0 line spacing
% Use the 'lineno' option for adding line numbers.
% The 'bestpractices' option for indicates that this is a best practices guide.
% Omit the bestpractices option to remove the marking as a LiveCoMS paper.
% Include "pubversion" option when the volume/article/DOI information is known
% Please note that these options may affect formatting.

@@

\begin{abstract}
This particular document provides a skeleton illustrating key sections for a Tutorial document.
Please see the sample \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates} for additional information on and examples of using the LiveCoMS LaTeX class.
Here we also assume familiarity with LaTeX and knowledge of how to include figures, tables, etc.; if you want examples, see the sample just referenced.

@@

\subsection{Scope}

Tutorials should endeavor to cover the specific task at hand, and also highlight how the steps might need to be modified (or additional care might need to be taken at particular points) to handle more general cases.

The scope of the tutorial, as well as the expected proficiencies / outcomes for researchers who complete the tutorial, should be clearly defined.
This will often happen in a specific section or subsection in the article itself.

@@

Here you would identify prerequisites/background knowledge that are assumed by your work, as well as any software/license requirements.

\subsection{Background knowledge}
Tutorials should clearly define what concepts or abilities researchers will need to complete the tutorial (e.g., some proficiency in Python; experience with Jupyter notebooks; knowledge of classical MD; etc).

\subsection{Software/system requirements}
Tutorials should clearly define what system and/or software requirements the researcher will need to complete the tutorial (e.g., VMD version 1.9 or newer, AMBER, etc.). Tutorials requiring specific software packages must provide instructions and files for the referenced version of the software.

\section{Content and links}

A tutorial will normally draw on additional files and materials; clearly indicate where and how these are available, with links, and how they are being archived for the long-term and maintained so they stay current.
You will likely want to reference your GitHub repository as a central point to access all of this information, and then the GitHub repository may link out to other content as needed.

\section{Checklists}
Tutorials do not necessarily require the use of a checklist as in Best Practices documents; however, they can include these if desired.
Several useful checklist formats are available, with examples presented in \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates}.
One example is shown here.

% Here is a single-column checklist that consists of multiple sub-checklists
\begin{Checklists}

\begin{checklist}{A list}
\textbf{Single-column checklists are also straightforward by removing the asterisk}
\begin{itemize}
\item First thing let's do an item which breaks across lines to see how that looks
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Another list}
\textbf{This is some further description.}
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\end{Checklists}
